Cover Your Basis: Comprehensive Data-Driven Characterization of the Binary Black Hole Population

### 2023-01-03 src/tex/appendicies.tex
maybe final fix?

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/spline_basis_plot.pdf}
        \caption{Plot showing a ``proper'' (see appendix \ref{sec:psplines}) normalized B-Spline basis of order 3 (cubic) with 20 degrees of freedom and equal weights for each component. 
        In black, we show the resulting spline function given equal weights and denote the location of the knots with gray x's.}
        \label{fig:spline_basis}
    \end{centering}
    \script{spline_basis_plot.py}
\end{figure}

@@

%One downside of this prior specification as noted in \citet{BayesianPSplines} and \citet{Jullion2007RobustSO}, is the dependence on 
%one's choice of value for the $b$ hyperparameter in the Gamma distribution for $\tau_\lambda$. The models introduced in \citet{Jullion2007RobustSO} show how 
%to alleviate this. W model $\tau_\lambda$ with a mixture model composed of multiple Gamma distributions each with varying values for $b$. 
%With this we now have the full prior on $\tau_\lambda$ as:

%\begin{align}
%    \bm{p} \sim \mathcal{D}(m) \\
%    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \Gamma(1, b_i)
%\end{align}

%\noindent Above $\mathcal{D}(m)$, denotes a Dirichlet distribution with $m$ degrees of freedom and ones as the concentration parameters, 
%and the $b_i$'s are $m$ different b shape parameters for the Gamma distribution.

%Additionally one can implement a spatially adaptive smoothing prior which allows for a smoothing prior
%that can smoothly evolve over the domain of your spline function. This is done in practice by having the $\tau_\lambda$ parameter evolve smoothly
%across the knots. \bruce{CITE BAYESIAN PSPLINES}, formulates a spatially adaptive prior in this way by adding in $n-r-1$ additional parameters that
%effectively modulate the $\tau_\lambda$ across each difference. We now replace our prior on the coeficients with:

%\begin{eqnarray}
%\bm{\lambda} \sim \mathcal{G}(\omega, \omega), \\
%\bm{\Lambda} \equiv \mathrm{diag}\big(1, \lambda_0,...,\lambda_{n-r-1}\big), \\
%p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{\Lambda} \bm{D_r} \bm{c} \big] e^{-n\bm{c}}
%\end{eqnarray}

%Where above the matrix $\bm{\Lambda}$ a diagonal matrix of shape $(n-r \times n-r)$, and $\omega$ an arbitrarily small value such that the Gamma distribution 
%prior on $\bm{\lambda}$ has a mean of 1 and an arbitrarily large variance. This enforces a smooth evolution of the smoothing penalty 
%across the domain that is being analyzed. This type of prior is especiially important when modeling distributions that span large orders of magnitude like 
%the power-law like mass distributions that are commonly used.

@@

\noindent
where above, we replaced the integrals over each event's likelihood with ensemble averages over $K_i$ posterior samples \citep{gwtc3DATA}. Above, $j$
indexes the $K_i$ posterior samples from each event and $\pi(\theta, z)$ is the default prior used by parameter estimations that 
produced the posterior samples for each event. In the analyses of GWTC-3, either the default prior used was uniform in detector frame masses, 
component spins and Euclidean volume or the posterior samples were re-weighted to such a prior before using them in our analysis. 
The corresponding prior evaluated in the parameters we hierarchically model, i.e. source frame primary mass, mass ratio, component spins and redshift is:

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figures/ppc_plot.pdf}
    \caption{Posterior predictive checks showing the CDFs of the observed (black) and predicted (red) distributions of GWTC-3 sized catalogs for each posterior sample of the IID spin B-Spline model. The shaded regions show 90\% credible intervals and the solid red line is the median of the predicted distribution.}
    \label{fig:ppc}
    \script{plot_ppcs.py}
\end{figure}

We follow the posterior predictive checking procedure done in recent population studies to validate our models inferences \citep{o3a_pop,Edelman_2022ApJ}. 
For each posterior sample describing our model's inferred population we reweigh the observed event samples and the found injections to that population and draw a set 69 (size of GWTC-3 BBH catalog) samples to construct the observed and predicted distributions we show in figure \ref{fig:ppc}. When the observed region stays encompassed within the predicted region the model is performing well, which we see across each of the fit parameters.

>>>>

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/spline_basis_plot.pdf}
        \caption{Plot showing a ``proper'' (see appendix \ref{sec:psplines}) normalized B-Spline basis of order 3 (cubic) with 20 degrees of freedom and equal weights for each component. 
        In black, we show the resulting spline function given equal weights and denote the location of the knots with gray x's. \LinkExplainer}
        \label{fig:spline_basis}
    \end{centering}
    \script{spline_basis_plot.py}
\end{figure}

@@

@@

\noindent
where above, we replaced the integrals over each event's likelihood with ensemble averages over $K_i$ posterior samples \citep{GWTC3DATA}. Above, $j$
indexes the $K_i$ posterior samples from each event and $\pi(\theta, z)$ is the default prior used by parameter estimations that 
produced the posterior samples for each event. In the analyses of GWTC-3, either the default prior used was uniform in detector frame masses, 
component spins and Euclidean volume or the posterior samples were re-weighted to such a prior before using them in our analysis. 
The corresponding prior evaluated in the parameters we hierarchically model, i.e. source frame primary mass, mass ratio, component spins and redshift is:

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figures/ppc_plot.pdf}
    \caption{Posterior predictive checks showing the CDFs of the observed (black) and predicted (red) distributions of GWTC-3 sized catalogs for each posterior sample of the IID spin B-Spline model. The shaded regions show 90\% credible intervals and the solid red line is the median of the predicted distribution. \LinkExplainer}
    \label{fig:ppc}
    \script{plot_ppcs.py}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{figures/spin_ppc_plot.pdf}
    \caption{Posterior predictive checks showing the CDFs of the observed (black) and predicted (red) distributions of GWTC-3 sized catalogs for each posterior sample of the IID spin B-Spline model. The shaded regions show 90\% credible intervals and the solid red line is the median of the predicted distribution. \LinkExplainer}
    \label{fig:spin_ppc}
    \script{plot_spin_ppcs.py}
\end{figure}

We follow the posterior predictive checking procedure done in recent population studies to validate our models inferences \citep{o3a_pop,Edelman_2022ApJ}. 
For each posterior sample describing our model's inferred population we reweigh the observed event samples and the found injections to that population and draw a set 69 (size of GWTC-3 BBH catalog) samples to construct the observed and predicted distributions we show in figure \ref{fig:ppc} and figure \ref{fig:spin_ppc}. When the observed region stays encompassed within the predicted region the model is performing well, which we see across each of the fit parameters.

### 2023-01-03 src/tex/conclusion.tex
add more citations in conclusions

The results presented in section \ref{sec:mass_dist} illustrate a wider mass distribution than inferred with power-law based models in \citet{o3b_astro_dist}, and a suppressed merger rate 
at low primary masses (i.e. $\leq8\msun$). While isolated formation is able to predict the $10\msun$ peak \citep{Antonini_2020}, cluster and dynamical formation scenarios struggle to predict 
a peak in the BH mass distribution less than $15-20\msun$ \citep{Hong_2018, Rodriguez_2019}. Globular cluster formation is expected to produce more top-heavy mass distributions than isolated 
and recent studies have shown suppressed BBH merger rates at lower ($m\leq15\msun$) masses when compared to predictions from the isolated channel \citep{Rodriguez_2015, Rodriguez_2019, BaveraMassTransfer,Belczynski_2016}. 
BBHs that form near active galactic nuclei (AGN) can preferentially produce higher mass black holes \citep{FordAGN, Tagawa_2021, Yang_2019}. 
We do not find any evidence for a truncation or rapid decline in the merger rate as a function of mass, that stellar evolution theory predicts due to pair-instability supernovae (PISNe) \citep{Heger_2002,PISN_Woosley,Heger_2003,Spera_2017}. The original motivation for the peak in the \textsc{PowerlawPeak} model \citep{Talbot_2018} was to represent a possible ``pileup'' of 
masses just before such truncation, since massive stars just light enough to avoid PISN will shed large amounts of mass in a series of ``pulses'' before collapsing to BHs in a process called 
pulsational pair-instability supernova (PPISN) \citep{Woosley_2017,Woosley_2019,Farmer_2019}. While the predictions of the mass scale where pair-instability kicks in are uncertain and depend on poorly understood physics 
like nuclear reaction rates of carbon and oxygen in the core of stars, models have a hard time producing this peak lower than $m\sim40\msun$ \citep{Belczynski_2016,Marchant_2019,Renzo_2020,Farmer_2019,Farmer_2020}. The lack of a truncation could 
point towards a higher prevalence of dynamical processes that can produce black holes in mass ranges stellar collapse cannot, such as hierarchical mergers of BHs \citep{Fishbach_2017,Doctor_2020,Kimball_genealogy,kimball2020evidence,doctor2021black,Fishbach_2022}, 
very low metallicity population III stars \citep{Belczynski_2020,Farrell_2020}, new beyond-standard-model physics\citep{Croon_newphysics,Sakstein_2020}, or black hole accretion of BHs in gaseous environments such as AGNs \citep{Secunda_2020,McKernan_2020,cruzosorio2021gw190521}.

>>>>

The results presented in section \ref{sec:mass_dist} illustrate a wider mass distribution than inferred with power-law based models in \citet{o3b_astro_dist}, and a suppressed merger rate 
at low primary masses (i.e. $\leq8\msun$), showing possible signs of binary selection effects or the purported low mass gap between neutron stars and black holes \citep{Fishbach_2020_mm,Farah_2022,NoPeaksWithoutValleys}. While isolated formation is able to predict the $10\msun$ peak \citep{Antonini_2020}, cluster and dynamical formation scenarios struggle to predict 
a peak in the BH mass distribution less than $15-20\msun$ \citep{Hong_2018, Rodriguez_2019}. Globular cluster formation is expected to produce more top-heavy mass distributions than isolated 
and recent studies have shown suppressed BBH merger rates at lower ($m\leq15\msun$) masses when compared to predictions from the isolated channel \citep{Rodriguez_2015, Rodriguez_2019, BaveraMassTransfer,Belczynski_2016}. 
BBHs that form near active galactic nuclei (AGN) can preferentially produce higher mass black holes \citep{FordAGN, Tagawa_2021, Yang_2019}. 
We do not find any evidence for a truncation or rapid decline in the merger rate as a function of mass, that stellar evolution theory predicts due to pair-instability supernovae (PISNe) \citep{Heger_2002,PISN_Woosley,Heger_2003,Spera_2017,Stevenson_2019}. The original motivation for the peak in the \textsc{PowerlawPeak} model \citep{Talbot_2018} was to represent a possible ``pileup'' of 
masses just before such truncation, since massive stars just light enough to avoid PISN will shed large amounts of mass in a series of ``pulses'' before collapsing to BHs in a process called 
pulsational pair-instability supernova (PPISN) \citep{Woosley_2017,Woosley_2019,Farmer_2019}. While the predictions of the mass scale where pair-instability kicks in are uncertain and depend on poorly understood physics 
like nuclear reaction rates of carbon and oxygen in the core of stars, models have a hard time producing this peak lower than $m\sim40\msun$ \citep{Belczynski_2016,Marchant_2019,Renzo_2020,Farmer_2019,Farmer_2020}. The lack of a truncation could 
point towards a higher prevalence of dynamical processes that can produce black holes in mass ranges stellar collapse cannot, such as hierarchical mergers of BHs \citep{Fishbach_2017,Doctor_2020,Kimball_genealogy,kimball2020evidence,doctor2021black,Fishbach_2022}, 
very low metallicity population III stars \citep{Belczynski_2020,Farrell_2020}, new beyond-standard-model physics\citep{Croon_newphysics,Sakstein_2020}, or black hole accretion of BHs in gaseous environments such as AGNs \citep{Secunda_2020,McKernan_2020,cruzosorio2021gw190521}.

### 2023-01-03 src/tex/results.tex

\begin{figure*}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/mass_distribution_plot.pdf}
        \caption{The marginal primary mass distribution inferred with the B-Spline model (red), with 64 knots spaced linearly in $\log m_1$, from 5\msun 
        to 100\msun. The solid line shows the population predictive distribution (PPD), and the shaded region 
        the 90\% credible interval. We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models 
        from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}.}
        \label{fig:mass_distribution}
    \end{centering}
    \script{mass_distribution_plot.py}
\end{figure*}

@@

\begin{figure}[ht!]
    \includegraphics[width=\linewidth]{figures/q_distribution_plot.pdf}
    \caption{The marginal mass ratio distribution inferred with the B-Spline model (red), with 18 knots spaced linearly in $q$, from 0.05 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
    We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}.}
    \label{fig:q_distribution}
    \script{q_distribution_plot.py}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}    
        \includegraphics[width=\linewidth]{figures/iid_spinmag.pdf}
        \caption{The spin magnitude distribution inferred with the B-Spline model (red) with 16 knots spaced linearly from 0 to 1, assuming the components are IID. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
        \label{fig:iid_spinmag_dist}
    \end{centering}
    \script{plot_iid_spinmag.py}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/ind_spinmag.pdf}
        \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the B-Spline model
        with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
        \label{fig:ind_spinmag_dist}
    \end{centering}
    \script{plot_ind_spinmag.py}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/iid_spintilt.pdf}
        \caption{The spin orientation distribution inferred with the B-Spline model (red) with 16 knots spaced linearly from -1 to 1, and assuming the components are IID. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
        \label{fig:iid_spintilt_dist}
    \end{centering}
    \script{plot_iid_spintilt.py}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/ind_spintilt.pdf}
        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the B-Spline model with 16 knots spaced linearly from -1 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
        \label{fig:ind_spintilt_dist}
    \end{centering}
    \script{plot_ind_spintilt.py}
\end{figure}

@@

\begin{figure*}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/effspin.pdf}
        \caption{The effective (left) and precessing (right) spin distributions inferred with the B-Spline IID spin model (red). The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. We show the inferred PPDs from the independent component spin B-Spline model (purple), and both the \textsc{Default} (blue) model and the 
        Gaussian (green) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
        \label{fig:eff_dist}
    \end{centering}
    \script{plot_effspin.py}
\end{figure*}

%\begin{figure}[ht!]
%    \begin{centering}
   %     \includegraphics[width=\linewidth]{figures/chi_p.pdf}
   %     \caption{The effective precessing spin distribution inferred with the B-Spline IID spin model (red). The solid line shows the population predictive %distribution (PPD), and the shaded region the 90\% credible interval. We show the inferred $\chi_\mathrm{p}$ 
   %     PPD from the independent component spin B-Spline model (purple), and both the \textsc{Default} (blue) model and the 
   %     Gaussian $\chi_\mathrm{p}$ (green) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
   %     \label{fig:chip_dist}
   % \end{centering}
   % \script{plot_chip.py}
% \end{figure}

@@

\begin{figure}[ht!]
    \includegraphics[width=\linewidth]{figures/rate_vs_z_plot.pdf}
    \caption{The BBH merger rate as a function of redshift. We show the B-Spline model (red) with 16 knots spaced linearly in $\log(z)$, 
    from the minimum to the maximum observed redshifts. The solid line shows the population predictive distribution (PPD), and the shaded region 
    the 90\% credible interval. We show the inferred 90\% credible interval from the \textsc{PowerlawRedshift} model 
    from the LVK's GWTC-3 population analyses in blue and a power law with exponent of 2.7 in gray, representing the expected star formation rate 
    \citep{Madau_2014, o3b_astro_dist}.}
    \label{fig:rofz}
    \script{rate_vs_z_plot.py}
\end{figure}

@@

\begin{figure}[ht!]
    \includegraphics[width=\linewidth]{figures/z_modulation_plot.pdf}
    \caption{The B-spline modulation to the underlying power law in redshift, (red). The solid line shows the population predictive distribution (PPD),
    and the shaded region the 90\% credible interval. We show the 90\% credible interval of the prior predictive distribution in dashed black lines.}
    \label{fig:z_modulation}
    \script{z_modulation_plot.py}
\end{figure}

>>>>

\begin{figure*}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/mass_distribution_plot.pdf}
        \caption{The marginal primary mass distribution inferred with the B-Spline model (red), with 64 knots spaced linearly in $\log m_1$, from 5\msun 
        to 100\msun. The solid line shows the population predictive distribution (PPD), and the shaded region 
        the 90\% credible interval. We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models 
        from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}. \LinkExplainer}
        \label{fig:mass_distribution}
    \end{centering}
    \script{mass_distribution_plot.py}
\end{figure*}

@@

\begin{figure}[ht!]
    \includegraphics[width=\linewidth]{figures/q_distribution_plot.pdf}
    \caption{The marginal mass ratio distribution inferred with the B-Spline model (red), with 18 knots spaced linearly in $q$, from 0.05 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
    We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}. \LinkExplainer}
    \label{fig:q_distribution}
    \script{q_distribution_plot.py}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}    
        \includegraphics[width=\linewidth]{figures/iid_spinmag.pdf}
        \caption{The spin magnitude distribution inferred with the B-Spline model (red) with 16 knots spaced linearly from 0 to 1, assuming the components are IID. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses. \LinkExplainer}
        \label{fig:iid_spinmag_dist}
    \end{centering}
    \script{plot_iid_spinmag.py}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/ind_spinmag.pdf}
        \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the B-Spline model
        with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses. \LinkExplainer}
        \label{fig:ind_spinmag_dist}
    \end{centering}
    \script{plot_ind_spinmag.py}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/iid_spintilt.pdf}
        \caption{The spin orientation distribution inferred with the B-Spline model (red) with 16 knots spaced linearly from -1 to 1, and assuming the components are IID. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses. \LinkExplainer}
        \label{fig:iid_spintilt_dist}
    \end{centering}
    \script{plot_iid_spintilt.py}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/ind_spintilt.pdf}
        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the B-Spline model with 16 knots spaced linearly from -1 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses. \LinkExplainer}
        \label{fig:ind_spintilt_dist}
    \end{centering}
    \script{plot_ind_spintilt.py}
\end{figure}

@@

\begin{figure*}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/effspin.pdf}
        \caption{The effective (left) and precessing (right) spin distributions inferred with the B-Spline IID spin model (red). The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. We show the inferred PPDs from the independent component spin B-Spline model (purple), and both the \textsc{Default} (blue) model and the 
        Gaussian (green) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses. \LinkExplainer}
        \label{fig:eff_dist}
    \end{centering}
    \script{plot_effspin.py}
\end{figure*}

@@

\begin{figure}[ht!]
    \includegraphics[width=\linewidth]{figures/rate_vs_z_plot.pdf}
    \caption{The BBH merger rate as a function of redshift. We show the B-Spline model (red) with 16 knots spaced linearly in $\log(z)$, 
    from the minimum to the maximum observed redshifts. The solid line shows the population predictive distribution (PPD), and the shaded region 
    the 90\% credible interval. We show the inferred 90\% credible interval from the \textsc{PowerlawRedshift} model 
    from the LVK's GWTC-3 population analyses in blue and a power law with exponent of 2.7 in gray, representing the expected star formation rate 
    \citep{Madau_2014, o3b_astro_dist}. \LinkExplainer}
    \label{fig:rofz}
    \script{rate_vs_z_plot.py}
\end{figure}

@@

\begin{figure}[ht!]
    \includegraphics[width=\linewidth]{figures/z_modulation_plot.pdf}
    \caption{The B-spline modulation to the underlying power law in redshift, (red). The solid line shows the population predictive distribution (PPD),
    and the shaded region the 90\% credible interval. We show the 90\% credible interval of the prior predictive distribution in dashed black lines. \LinkExplainer}
    \label{fig:z_modulation}
    \script{z_modulation_plot.py}
\end{figure}
